Fisher vector places: learning compact descriptors for place recognition

### 2014-11-13 cvpr15review.tex
text edit: results, conclusions, table spit: captions, plot: fixed BOW to SURF

% usepackages by Petr
\usepackage{epstopdf}
\usepackage{enumerate}
\usepackage{subfigure}
\usepackage{caption}
\usepackage{tabularx}
\usepackage[table]{xcolor}

@@

      \textcolor{petr}{
        The proposed re-normalization procedure can be interpreted as a simple form of affine calibration where the uncalibrated SVM score $s(x)=w^T x+b$ is transformed into a calibrated score $f(x)=\alpha s(x)+\beta$, where $\alpha = 1/||w||$ and $\beta = -b\alpha$. Note that the bias term b is not ignored but used to compute $f(x)$. The intuition is that for L2 normalized descriptors x computing the calibrated score $f(x)$ corresponds to computing the normalized cross-correlation between vectors w and x. This was found to work well in retrieval (see e.g. Sivic and Zisserman, ICCV 2003 [32]) or matching whitened HOG descriptors [11,13] (see e.g. [Doersch et al., Mid-Level Visual Element Discovery as discriminative Mode Seeking, NIPS 2013]), but has not yet been used in conjunction with SVMs as done in this work. Note also that the affine calibration can be computed offline and does not need any additional computation or storage at query time compared to the p-value calibration of Gronat et al. [12].
      }

@@

   \subsection{Experimental set-up}
      We perform experiments on a database of Google Street View images of Pittsburgh downloaded from the Internet. The data contains panoramas covering roughly an area of $1.3 \times 1.2 \; {\rm km}^2$.       
      Similar to~\cite{Chen11}, for each panorama we generate 12 overlapping perspective views corresponding to two different elevation angles to capture both the street-level scene and the building fa\c{c}ades, resulting in a total of 24 perspective views each with $90^\circ$ FOV and resolution of $960 \times 720$ pixels.
      For evaluation we have used two versions of this data. The first one was obtained from the authors of~\cite{Gronat13} ($25$k images). In the second version we download additional images to increase the dataset size to $55$k images. 
      As a query set with known ground truth GPS positions, we use the 8999 panoramas from the Google Street View research dataset. This dataset covers approximately the same area, but has been captured at a different time, and depicts the same places from different viewpoints and under different illumination conditions. For each test panorama, we generate a set of perspective images as described above. Finally, we randomly select out of all generated perspective views a subset of 4k images, which is used as a test set to evaluate the performance of the proposed approach.
      Since all the query images have associated GPS location we can compute their spatial distance from the database images returned by the matching method. We consider a query image to be correctly localized if the retrieved database image lies within a perimeter of $20m$ from the location of the query.
      %
      \begin{figure}[t!]
         \centering
         \includegraphics[width=\linewidth]{imgs/plotPitt25k}    
         \caption{
            \textbf{Evaluation on Pittsburgh 25k \cite{Gronat13} dataset.} The fraction of correctly recognized queries (recall@K, y-axis) vs. the number of top $K$ retrieved database images for different Fisher vector dimensions. The learnt descriptors by the proposed method (FV e-SVM) consistently improve over the raw Fisher vector descriptors across the whole range of $K$  and all dimensions.
         }
         \label{fig:recall}
      \end{figure}

@@

   \subsection{Results}    
      For each database (Pittsburgh 25k and Pittsburgh 55k) we compare results of our method (FV e-SVM) to two baselines: standard bag-of-visual-words baseline (BOW) and raw Fisher vector matching without learning (FV).

@@

      \paragraph{Applying the proposed method to other descriptors}
        \textcolor{petr}{TODO:  
          Applying the proposed method to other descriptors (R18, R38) The proposed approach can be applied to other descriptors beyond Fisher vectors. To demonstrate this we have applied the proposed calibration by re-normalization to the bag-of-visual-words descriptor used in (Gronat et al.[12]) and observed improvement from 29.4\% recall@K=1 (vanilla bag-of-visual-words) to 32.6\% recall@K=1 (e-SVM with the proposed calibration by renormalization). For bag-of-visual-words, the e-SVM with p-value calibration gives comparable results (33.6\% recall@K=1) but at an increased training cost and a significantly higher required memory footprint at query time, which makes the method very hard to scale-up to database sizes beyond 200k images.
        }

@@

        \textcolor{petr}{ TODO:
          We have compared the proposed method with the p-value calibration of (Gronat et al.[12]) applied to Fisher vectors. The results show that our method significantly outperforms the p-value calibration (37.8\% recall@1 vs. 32.3\% recall@1; 56.9\% recall@5 vs. 50.0\% recall@5) for the Fisher vector of dimension 128. Similar gains are observed for other FV dimensions.
        }
      \paragraph{Memory complexity analysis.}
         Figure~\ref{fig:memory} compares the performance of the learnt discriminative descriptor (FV eSVM) to the raw Fisher vectors (FV) for different target dimensions. 
         The results demonstrate that for a given level of accuracy (y-axis) our method learns a more compact (lower-dimensional) representation (x-axis). For example, our learnt 128-dimensional descriptor achieves a similar accuracy (around 65\%) to the 256-dimensional raw Fisher descriptor essentially reducing the memory complexity to 50\% for the same level of performance.  Note that 
         similar to~\cite{Jegou12}, we observe decrease in performance at high-dimensions for both the baseline and our method.
         %
         \begin{figure}[t!]
            \centering
            \includegraphics[width=1.0\linewidth]{imgs/FVmemory}    
            \caption{
               \textbf{Memory complexity analysis.} 
               The fraction of correctly localized queries at the top 10 retrieved images (y-axis) for different Fisher vector dimensions (x-axis). The learnt descriptors by our method (FV e-SVM) clearly outperform the raw Fisher vector descriptors (FV) for all dimensions. Note that for a certain level of performance (y-axis) the proposed method learns a more memory efficient (lower dimensional, x-axis) descriptor.
            }
            \label{fig:memory}
         \end{figure}
         %
         %
         %
         \begin{figure*}
            \include{myFigureWnorm}
            \caption{
                \textbf{Examples of correctly and incorrectly localized queries for the learnt Fisher vector representation.}
                Each example shows a query image (left) together with correct (green) and incorrect (red) matches from the database obtained by the learnt Fisher vector representation \emph{w-norm} method (top) and the standard Fisher vector baseline (bottom) for dimension 128. Note that the proposed method is able to recognize the place depicted in the query image despite changes in viewpoint, illumination and partial occlusion by other objects (trees, lamps) and buildings. 
                Note that the baseline methods often finds images depicting the same buildings but in a distance whereas our learnt representation often finds a closer view better matching the content of the query.       
            }
            \label{fig:images}
         \end{figure*}
         %
         %
         %
         \begin{table*}[t!]
            \begin{centering}
               \begin{tabularx}{0.75\linewidth}{|l|c c c c c|c c c c c|}
                  \hline 
                  \rowcolor{maroon!50}
                  Method: & \multicolumn{5}{c|}{25k Pittsburgh} & \multicolumn{5}{c|}{55k Pittsburgh} \\
                  \hline 
                  \hline 
                  \rowcolor{maroon!50}
                  recall@K [$\%$] & 1 & 2 & 5 & 10 & 20 & 1 & 2 & 5 & 10 & 20\\
                  \hline
                  \rowcolor{maroon!10}
                  BOW         & 29.4 & 35.7 & 47.0 & 57.1 & 66.5 & 8.7 & 11.0 & 17.3 & 22.8 & 25.4  \\
                  BOW raw SVM & 6.4  &  8.1 & 13.5 & 17.5 & 20.5 & & & & & \\ 
                  BOW e-SVM   & 32.2 & 37.3 & 46.2 & 54.4 & 63.3 & & & & & \\
                    \hline
                  \rowcolor{maroon!10}
                  FV128         & 33.6 & 41.8 & 52.0 & 59.8 & 67.7 & 10.9 & 14.1 & 20.2 & 26.4 & 33.2 \\
                  FV128 raw SVM & 32.4 & 41.1 & 52.6 & 60.4 & 68.4 & & & & & \\
                  \rowcolor{maroon!10}
                  \textbf{FV128 e-SVM}   & \textbf{37.8}  & \textbf{46.1} & \textbf{56.9} & \textbf{64.9} & \textbf{72.6}  &
                                             \textbf{13.5}  &  \textbf{17.7}  &  \textbf{25.0}  &  \textbf{31.8}  &  \textbf{39.0} \\
                    \hline
                    \rowcolor{maroon!10}
                    FV512         & 44.3 & 51.7 & 61.4 & 68.7 & 75.2 & 17.3 &  21.1 &  28.4 &  34.2 &  40.3 \\
                    \rowcolor{maroon!10}
                    \textbf{FV512 e-SVM}   & \textbf{47.6}  & \textbf{55.4} & \textbf{65.1} & \textbf{72.4} & \textbf{78.8}  &
                                             \textbf{19.8} &  \textbf{25.1} &  \textbf{32.7}  & \textbf{38.7} &  \textbf{46.0} \\
                    \hline
                  \rowcolor{maroon!10}
                  FV2048        & 46.9  & 54.1 & 63.8 & 70.5 & 76.8 & 19.2 & 23.5 & 29.9 &  35.2 &  41.9 \\
                  \rowcolor{maroon!10}
                  \textbf{FV2048 e-SVM}  & \textbf{50.2} & \textbf{57.3} & \textbf{67.0} & \textbf{73.8} & \textbf{78.0} &
                    \textbf{20.8} & \textbf{25.9} & \textbf{33.1} & \textbf{38.7} & \textbf{45.9}\\
                  \hline
               \end{tabularx}
            \caption{ \textcolor{myRed}{}
                  The fraction of correctly recognized queries (recall@K) vs. the number of top $K\in\{1,2,5,10,20\}$ retrieved database images for different Fisher vector dimensions $d\in\{128,512,2048\}$. The learnt descriptors by the proposed method (FV e-SVM) consistently improve over the raw Fisher vector descriptors across the whole range of $K$  and all dimensions on both the 25k and 55k Pittsburgh image datasets.     
            }
            \label{tab:recall}
            \end{centering}
         \end{table*}
         %
         %
         %
         % \begin{figure*}[t!]
         %    %%%%%%%%%%% Example 1 %%%%%%%%%%%%%%%
         %    % QUERY image
         %    \begin{minipage}{0.34\linewidth}
         %       \centering
         %       \vspace{5mm}
         %       \includegraphics[height=40mm]{imgs/ex1/query.jpg}
         %    \end{minipage}
         %    % Retrieved images
         %    \begin{minipage}{0.75\linewidth}
         %       % FV e-SVM
         %       \begin{minipage}{\linewidth} 
         %           \colorbox{myGreen}{\includegraphics[height=16mm]{imgs/ex1/FVsvm1.jpg}}
         %           \colorbox{myGreen}{\includegraphics[height=16mm]{imgs/ex1/FVsvm2.jpg}}
         %           \colorbox{myGreen}{\includegraphics[height=16mm]{imgs/ex1/FVsvm3.jpg}}
         %           \colorbox{myGreen}{\includegraphics[height=16mm]{imgs/ex1/FVsvm4.jpg}}
         %       \end{minipage}
         %       \\
         %       \begin{minipage}{\linewidth}
         %           \colorbox{myRed}{\includegraphics[height=16mm]{imgs/ex1/FV1.jpg}}
         %           \colorbox{myRed}{\includegraphics[height=16mm]{imgs/ex1/FV2.jpg}}
         %           \colorbox{myRed}{\includegraphics[height=16mm]{imgs/ex1/FV3.jpg}}
         %           \colorbox{myRed}{\includegraphics[height=16mm]{imgs/ex1/FV4.jpg}}
         %       \end{minipage} 
         %    \end{minipage}
         %    \\
         %    %%%%%%%%%%% Example 2 %%%%%%%%%%%%%%%
         %    \begin{minipage}{0.34\linewidth}
         %       \centering
         %       \vspace{0mm}
         %       \includegraphics[height=36mm]{imgs/ex2/query.jpg}
         %    \end{minipage}
         %    % Retrieved images
         %    \begin{minipage}{0.75\linewidth}
         %       % FV e-SVM
         %       \begin{minipage}{\linewidth} 
         %           \colorbox{myGreen}{\includegraphics[height=16mm]{imgs/ex2/FVsvm1.jpg}}
         %           \colorbox{myGreen}{\includegraphics[height=16mm]{imgs/ex2/FVsvm2.jpg}}
         %           \colorbox{myGreen}{\includegraphics[height=16mm]{imgs/ex2/FVsvm3.jpg}}
         %           \colorbox{myGreen}{\includegraphics[height=16mm]{imgs/ex2/FVsvm4.jpg}}
         %       \end{minipage}
         %       \\
         %       \begin{minipage}{\linewidth}
         %           \colorbox{myRed}{\includegraphics[height=16mm]{imgs/ex2/FV1.jpg}}
         %           \colorbox{myRed}{\includegraphics[height=16mm]{imgs/ex2/FV2.jpg}}
         %           \colorbox{myRed}{\includegraphics[height=16mm]{imgs/ex2/FV3.jpg}}
         %           \colorbox{myRed}{\includegraphics[height=16mm]{imgs/ex2/FV4.jpg}}
         %       \end{minipage} 
         %    \end{minipage}
         %    \vspace{3mm}
         %    \\
         %    %%%%%%%%%%% Example 3 %%%%%%%%%%%%%%%
         %    \begin{minipage}{0.34\linewidth}
         %       \centering
         %       \vspace{0mm}
         %       \includegraphics[height=36mm]{imgs/ex3/query.jpg}
         %    \end{minipage}
         %    % Retrieved images
         %    \begin{minipage}{0.75\linewidth}
         %       % FV e-SVM
         %       \begin{minipage}{\linewidth} 
         %           \colorbox{myGreen}{\includegraphics[height=16mm]{imgs/ex3/FVsvm1.jpg}}
         %           \colorbox{myRed}{\includegraphics[height=16mm]{imgs/ex3/FVsvm2.jpg}}
         %           \colorbox{myGreen}{\includegraphics[height=16mm]{imgs/ex3/FVsvm5.jpg}}
         %           \colorbox{myGreen}{\includegraphics[height=16mm]{imgs/ex3/FVsvm4.jpg}}
         %       \end{minipage}
         %       \\
         %       \begin{minipage}{\linewidth}
         %           \colorbox{myRed}{\includegraphics[height=16mm]{imgs/ex3/FV1.jpg}}
         %           \colorbox{myGreen}{\includegraphics[height=16mm]{imgs/ex3/FV2.jpg}}
         %           \colorbox{myRed}{\includegraphics[height=16mm]{imgs/ex3/FV3.jpg}}
         %           \colorbox{myRed}{\includegraphics[height=16mm]{imgs/ex3/FV4.jpg}}
         %       \end{minipage} 
         %    \end{minipage}
         %    \vspace{3mm}
         %    \\
         %    %%%%%%%%%%% Example 4 %%%%%%%%%%%%%%%
         %    \begin{minipage}{0.34\linewidth}
         %       \centering
         %       \vspace{0mm}
         %       \includegraphics[height=36mm]{imgs/ex4/query.jpg}
         %    \end{minipage}
         %    % Retrieved images
         %    \begin{minipage}{0.75\linewidth}
         %       % FV e-SVM
         %       \begin{minipage}{\linewidth} 
         %           \colorbox{myGreen}{\includegraphics[height=16mm]{imgs/ex4/FVsvm1.jpg}}
         %           \colorbox{myRed}{\includegraphics[height=16mm]{imgs/ex4/FVsvm2.jpg}}
         %           \colorbox{myGreen}{\includegraphics[height=16mm]{imgs/ex4/FVsvm5.jpg}}
         %           \colorbox{myGreen}{\includegraphics[height=16mm]{imgs/ex4/FVsvm4.jpg}}
         %       \end{minipage}
         %       \\
         %       \begin{minipage}{\linewidth}
         %           \colorbox{myRed}{\includegraphics[height=16mm]{imgs/ex4/FV1.jpg}}
         %           \colorbox{myGreen}{\includegraphics[height=16mm]{imgs/ex4/FV2.jpg}}
         %           \colorbox{myRed}{\includegraphics[height=16mm]{imgs/ex4/FV3.jpg}}
         %           \colorbox{myRed}{\includegraphics[height=16mm]{imgs/ex4/FV4.jpg}}
         %       \end{minipage} 
         %    \end{minipage}
         %    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
         %    \caption{
         %       Each example shows a query image (left) together with correct (green) and incorrect (red) matches from the database obtained by our learnt descriptors (top) and the raw Fisher vector descriptor baseline (bottom). For each method we show the top 4 matches from the database using 128-dimensional descriptors.        
         %    }
         %    \label{fig:images}
         % \end{figure*}
         %
         %
         %
   \section{Conclusions}
      We have shown that a discriminative yet compact image representation for place recognition can be learnt using the exemplar support vector machine applied to Fisher vector image descriptors without the need for expensive and tedious calibration typical for other exemplar  support vector machine methods. 
      \textcolor{petr}{We demonstrate that proposed method is applicable to two different descriptors, the bag-of-visual-words and Fisher vectors.}
      Our results show significant gains in place recognition performance compared to raw Fisher vector matching as well as other baselines. Our work opens-up the possibility of learning a compact and discriminative representation using other descriptors such as HOG~\cite{Dalal05} or the recently developed convolutional neural network features~\cite{Donahue13,Krizhevsky12,Oquab14,Sermanet13} as well as extending the analysis to other cost functions~\cite{Gharbi12,Hariharan12}.

>>>>

% usepackages by Petr
\usepackage{epstopdf}
\usepackage{enumerate}
\usepackage{subfigure}
\usepackage{caption}
\usepackage{tabularx}
\usepackage[table]{xcolor}
\usepackage{hyphenat}

@@

      \textcolor{petr}{%TODO: \emph{we should't speak about calibration, we shoud address not ignoring $b$}\\
         Notice that even the new descriptor $\Phi_j$ is obtained by normalization of the learnt hyperplane $w_j$, the bias $b$ form equation~\eqref{eq:decomposed} is not ignored. Indeed, the bias term in convex objective~\eqref{eq:obj} is affecting the learnt the hyperplane.
         %\\
         %The proposed re-normalization procedure can be interpreted as a simple form of affine calibration where the uncalibrated SVM score $s(x)=w^T x+b$ is transformed into a calibrated score $f(x)=\alpha s(x)+\beta$, where $\alpha = 1/||w||$ and $\beta = -b\alpha$. Note that the bias term b is not ignored but used to compute $f(x)$. The intuition is that for L2 normalized descriptors x computing the calibrated score $f(x)$ corresponds to computing the normalized cross-correlation between vectors w and x. This was found to work well in retrieval (see e.g. Sivic and Zisserman, ICCV 2003 [32]) or matching whitened HOG descriptors [11,13] (see e.g. [Doersch et al., Mid-Level Visual Element Discovery as discriminative Mode Seeking, NIPS 2013]), but has not yet been used in conjunction with SVMs as done in this work. Note also that the affine calibration can be computed offline and does not need any additional computation or storage at query time compared to the p-value calibration of Gronat et al. [12].
      }

@@

   \subsection{Experimental set-up}
      We perform experiments on a database of Google Street View images of Pittsburgh downloaded from the Internet. The data contains panoramas covering roughly an area of $1.3 \times 1.2 \; {\rm km}^2$.       
      Similar to~\cite{Chen11}, for each panorama we generate 12 overlapping perspective views corresponding to two different elevation angles to capture both the street-level scene and the building fa\c{c}ades, resulting in a total of 24 perspective views each with $90^\circ$ FOV and resolution of $960 \times 720$ pixels.
      For evaluation we have used two versions of this data. The first one was obtained from the authors of~\cite{Gronat13} ($25$k images). In the second version we download additional images to increase the dataset size to $55$k images. 
      As a query set with known ground truth GPS positions, we use the 8999 panoramas from the Google Street View research dataset. This dataset covers approximately the same area, but has been captured at a different time, and depicts the same places from different viewpoints and under different illumination conditions. For each test panorama, we generate a set of perspective images as described above. Finally, we randomly select out of all generated perspective views a subset of 4k images, which is used as a test set to evaluate the performance of the proposed approach.
      Since all the query images have associated GPS location we can compute their spatial distance from the database images returned by the matching method. We consider a query image to be correctly localized if the retrieved database image lies within a perimeter of $20m$ from the location of the query.
      %
      \begin{figure}[t!]
         \centering
         \includegraphics[width=\linewidth]{imgs/plotPitt25kSURF}    
         \caption{
            \textbf{Evaluation on Pittsburgh 25k \cite{Gronat13} dataset.} The fraction of correctly recognized queries (recall@K, y-axis) vs. the number of top $K$ retrieved database images for different Fisher vector dimensions. The learnt descriptors by the proposed method (FV e-SVM) consistently improve over the raw Fisher vector descriptors across the whole range of $K$  and all dimensions.
         }
         \label{fig:recall}
      \end{figure}

@@

   \subsection{Results}  
      \textcolor{petr}{TODO: comment results from the table - raw SVM BOW/FV}  
      For each database (Pittsburgh 25k and Pittsburgh 55k) we compare results of our method (FV e-SVM) to two baselines: standard bag-of-visual-words baseline (BOW) and raw Fisher vector matching without learning (FV).

@@

      \paragraph{Applying the method to other descriptors.}
        \textcolor{petr}{ 
          The proposed approach can be applied to other descriptors beyond Fisher vectors. To demonstrate this we have applied the proposed method to the bag-of-visual-words descriptor and observed improvement from 28.7\% recall@K=1 (vanilla bag-of-visual-words) to 31.8\% recall@K=1 (e-SVM). For bag-of-visual-words, the e-SVM with p-value calibration gives comparable results (33.6\% recall@K=1) but at an increased training cost and a significantly higher required memory footprint at query time, which makes the method very hard to scale-up to database sizes beyond 200k images.
        }

@@

        \textcolor{petr}{
         We also performed p-val calibration proposed by Gronat et al.~\cite{Gronat13} on e-SVM Fisher vectors. We found that the calibration did not perform for the learnt Fisher vector classifiers (top 1 recall of 25.3\% compared to baseline performance of 33.6\% for dimension 128). When examining the results, we believe this may be attributed to the fact that Fisher vectors are low dimensional compared to the extremely high-dimensional (d=100,000) bag-of-visual-words representation, which affects the distribution of the classifier scores on the negative test data. 
          %We have compared the proposed method with the p-value calibration of (Gronat et al.[12]) applied to Fisher vectors. The results show that our method significantly outperforms the p-value calibration (37.8\% recall@1 vs. 32.3\% recall@1; 56.9\%recall@5 vs. 50.0\% recall@5) for the Fisher vector of dimension 128. Similar gains are observed for other FV dimensions.
        }
      \paragraph{Memory complexity analysis.}
         Figure~\ref{fig:memory} compares the performance of the learnt discriminative descriptor (FV eSVM) to the raw Fisher vectors (FV) for different target dimensions. 
         The results demonstrate that for a given level of accuracy (y-axis) our method learns a more compact (lower-dimensional) representation (x-axis). For example, our learnt 128-dimensional descriptor achieves a similar accuracy (around 65\%) to the 256-dimensional raw Fisher descriptor essentially reducing the memory complexity to 50\% for the same level of performance.  Note that 
         similar to~\cite{Jegou12}, we observe decrease in performance at high-dimensions for both the baseline and our method.
         %
         \begin{figure}[t!]
            \centering
            \includegraphics[width=1.0\linewidth]{imgs/FVmemory}    
            \caption{
               \textbf{Memory complexity analysis.} 
               The fraction of correctly localized queries at the top 10 retrieved images (y-axis) for different Fisher vector dimensions (x-axis). The learnt descriptors by our method (FV e-SVM) clearly outperform the raw Fisher vector descriptors (FV) for all dimensions. Note that for a certain level of performance (y-axis) the proposed method learns a more memory efficient (lower dimensional, x-axis) descriptor.
            }
            \label{fig:memory}
         \end{figure}
         \begin{table}[htb]
            \begin{centering}
               \include{table25k}
            \caption{ \textbf{Results on Pittsburgh 25k dataset.}
                  The fraction of correctly recognized queries (recall@K)
                  \textcolor{petr}{
                     in top $K\in\{1,2,5,10,20\}$ retrieved images.
                     Different methods have been applied to two types of descriptors, the BOW and Fisher vectors compressed to different dimensions.The learnt representations (BOW \emph{e-SVM} and BOW \emph{p-val}) outperform the raw BOW baseline as well as the learnt representation without calibration (BOW raw SVM).
                  } 
                  The learnt descriptors by the proposed method (FV e-SVM) consistently improve over the raw Fisher vector descriptors across the whole range of $K$  and all dimensions on both the 25k and 55k Pittsburgh image datasets.     
            }
            \label{tab:recall}
            \end{centering}
         \end{table}

         \begin{table}[htb]
            \begin{centering}
               \include{table55k}
               \caption{ \textbf{Results on Pittsburgh 55k dataset.}
                  The fraction of correctly recognized queries (recall@K)
                  \textcolor{petr}{
                  in top $K\in\{1,2,5,10,20\}$ retrieved images.
                  The proposed method (\emph{e-SVM}) has been applied to Fisher vectors compressed to different dimensions.
                  } 
                  The learnt descriptors by the proposed method (FV e-SVM) consistently improve over the raw Fisher vector descriptors across the whole range of $K$  and all dimensions on both the 25k and 55k Pittsburgh image datasets.     
               }
            \label{tab:recall2}
            \end{centering}
         \end{table}
         %
         %
         %
         \begin{figure*}[h]
            \include{myFigureWnorm}
            \caption{
                \textbf{Examples of correctly and incorrectly localized queries for the learnt Fisher vector representation.}
                Each example shows a query image (left) together with correct (green) and incorrect (red) matches from the database obtained by the learnt Fisher vector representation \emph{w-norm} method (top) and the standard Fisher vector baseline (bottom) for dimension 128. Note that the proposed method is able to recognize the place depicted in the query image despite changes in viewpoint, illumination and partial occlusion by other objects (trees, lamps) and buildings. 
                Note that the baseline methods often finds images depicting the same buildings but in a distance whereas our learnt representation often finds a closer view better matching the content of the query.       
            }
            \label{fig:images}
         \end{figure*}
         %
         %
         %

   \section{Conclusions}
      We have shown that a discriminative yet compact image representation for place recognition can be learnt using the exemplar support vector machine applied to Fisher vector image descriptors without the need for expensive and tedious calibration typical for other exemplar  support vector machine methods. 
      \textcolor{petr}{We demonstrate that proposed method is applicable to two different descriptors, the bag-of-visual-words and Fisher vectors.}
      Our results show significant gains in place recognition performance compared to raw Fisher vector matching as well as other baselines. Our work opens-up the possibility of learning a compact and discriminative representation using other descriptors such as HOG~\cite{Dalal05} or the recently developed convolutional neural network features~\cite{Donahue13,Krizhevsky12,Oquab14,Sermanet13} as well as extending the analysis to other cost functions~\cite{Gharbi12,Hariharan12}.
